---
title: ""
output: 
  html_document: 
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::read_chunk("../../global.R")
```
```{r global, echo=FALSE}
```

## Lockdown browser + Webcam instruction
  - You must stay on camera for the entire exam.
  - Please dress appropriately, as though you are taking the exam in class.
  - You should not be laying on a bed / should be sitting at a desk/table as you would in a classroom.
  - The camera must not be covered at any time nor may the microphone be muted.
  - The camera must be pointing at your face all the time and not be tilted to any other direction.
  - It is your responsibility to ensure that the computer you are working on is configured properly. Complete the system check prior to taking the exam.
  - Failure to comply with the environment scan instructions will result in an invalidation of your exam score. 
  - Grades will be muted until after I review all of the Respondus exam videos. Please refer to the student code of conduct as well as our syllabus where behavior that constitutes cheating is described.