---
title: "Assignment 3 - Data extraction"
output: 
  html_document: 
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::read_chunk("../../global.R")
```
```{r global, echo=FALSE}
```

In this assignment, you will write SELECT queries to extract data records from the SRECORD database from Assignment 2.

You now have access to this schema. On the SQL Developer Web, search the navigational panel for SRECORD.

- To search for a schema: on the navigation pane, click the box on which your WSU ID, and enter the name of the schema to search, which in this case "SRECORD"
- To access tables on the schema: put the schema name and dot (.) in front of the name of the table from which to extract data; e.g., to select the ALBUM table in the SRECORD schema, you must enter `SELECT * FROM SRECORD.ALBUM;` not `SELECT * FROM ALBUM;`

# Submission guidelines

- Deliverable: submit your query for each question
  - one query per question
  - Submit queries only. **Do not include any narratives nor outputs.**
- Resubmit as many times as you want. The assignment will remain open until the due date.
- Your queries must use the SRECORD schema. 
- A late submission will result in 5% point reduction per day, and any submission over five days late will not be accepted. See course policy for details.

# Problems

Using the SRECORD schema, write SELECT queries to answer the following questions:

1. List the name of all artists.
2. Get the ID and title of albums whose price is above 5 dollars.
3. List the ID and name of customers living in Michigan.
4. List the ID and date of orders made by Cash.
5. Get the ID, date, and subscription option of all digital orders.
6. Get all customer information (*) for those who purchased the annual subscription.
7. Which state do customers live who chose the expedite delivery? (Suppress duplicates)
8. Which song was played the most? List songs with song titles, artist names, and play counts in descending order of the play count
9. Which album was sold the most? List albums with album titles, release dates, and quantities ordered in descending order of the quantities ordered.
10. Who is the most played artist? List artist names and play count of songs written by the artists in descending order of the play count.
11. What are the average prices of albums delivered by Free, Standard, and Expedite shipping?
 

