---
title: "Final exam instructions"
output: 
  html_document: 
    theme: cosmo
    includes:
      after_body: ../misc/lockdown_short_instructions.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::read_chunk("../../global.R")
```
```{r global, echo=FALSE}
```

## Logistics
- Exam schedule: 9:00 AM on 5/1 - 11:59 PM on 5/2
- Time limit: 2 hours. You can take any 2-hour window during that period.
- You must start before 9:59 pm on 11/15 to use the full 2 hours.
  - After 9:59 pm, you can still take the exam, but the time allowed you will be less than 2 hours.
  - After 11:59 pm, you won't be able to make any attempt.
- A session will be automatically saved and terminated upon the time limit. Once you start, the timer won't stop even if you leave the exam page.
- Closed-book exam. No crib sheet allowed.

## Two-part exams
- Multiple choice questions: 22 questions * 2 points = 44 points
- SQL questions: 7 questions, 56 points
  - Similar to Assignment 3 and the mock exam
  - An ERD and table definition will be provided. 
  - Your queries must follow the Oracle SQL syntax. Partial credit will be given based on your answer if it fails to run.
  - **Have your SDW credentials ready as you will be using Lockdown Browser**
    - To access your SDW, click your WSU ID from the list on the next page
  - **Data schema: finalexam**
    - To view the schema and its tables, click the box with your WSU ID on it, and search for "finalexam" 
    - To select a table from the schema, you must put "finalexam." in front of the name of the table to which you're referring. E.g., select * from finalexam.aliases (not select * from aliases)
  - **Write one SELECT query per question**
    - Test your query on SDW, and copy and paste it onto Canvas