---
title: "SDW Tutorial 1"
output: 
  html_document: 
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::read_chunk("../../global.R")
```
```{r global, echo=FALSE}
```


# Access SQL Developer Web (SDW)

To access the Oracle server that hosts your database, we are going to use a client program called "SQL Developer Web." This program is web-based, so you don't need to install anything but simply enter the URL and log in.

**1. Each user has a different URL to SQL Developer Web:**

The below URL that is replaced with your WSU ID will be your unique URL.

`https://wq1mqvljkclf5te-db202003171615.adb.us-ashburn-1.oraclecloudapps.com/ords/your_WSU_ID/_sdw/?nav=worksheet`

e.g., if your WSU ID is ab1234, then the access URL will be

`https://wq1mqvljkclf5te-db202003171615.adb.us-ashburn-1.oraclecloudapps.com/ords/ab1234/_sdw/?nav=worksheet`

**2. Enter Username and Password:**

Username: your WSU ID
Password: sent to your email.

You will receive an email from me that contains your log-in credentials and unique access URL.

# Sign In and Workspace Tour

<br>

<iframe width="800" height="450" src="https://www.youtube.com/embed/vQQbl1GziKI" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen data-external="1"></iframe>  
